Stellar Radiation is Critical for Regulating Star Formation and Driving Outflows in Low Mass Dwarf Galaxies

### 2019-04-03 thesis/chapters/ch_chapter4.tex
Final plot size shifting for chapters. Fixing ch1 figure labels.

\begin{figure*}
\centering
\includegraphics[width=0.45\linewidth]{figures/ch4/AGB1_enrichment_evolution_average_CGM}
\includegraphics[width=0.45\linewidth]{figures/ch4/NSNS1_enrichment_evolution_average_CGM} \\
\includegraphics[width=0.45\linewidth]{figures/ch4/SNE1_enrichment_evolution_average_CGM}
\includegraphics[width=0.45\linewidth]{figures/ch4/HNE1_enrichment_evolution_average_CGM}
\caption{Time evolution of the }
\label{ch4:fig:ISM_CGM}
\end{figure*}

@@

However, the metals from each source do gradually trend towards a fraction of $\sim$0.8 by the end of the 150~Myr simulation time, corresponding to the mass fraction of the CNM at this point in the galaxy's evolution (see Figure~\ref{ch1:figISM_evolution}). This trend -- that the fraction of metals contained in a given phases tends towards the mass fraction of that phase -- is true across all phases in the simulation. Therefore, we can consider that the metals for each source are well-mixed across the \textit{phases} of the ISM on timescales of $\sim$100-150~Myr. This is comparable, but less than, the dynamical timescale of the galaxy, $\sim$200~Myr. These two results suggest that the delay-time between when metals are available to enrich ongoing star formation is on order of $\sim$10~Myr across sources, and only significant for the lowest (E46, AGB-like) energy sources. Although well-mixed across phases, we emphasize that this does not imply that the abundances are the same across phases nor that the metals are spatially well-mixed across the galaxy. We investigate this second point further below.

@@

 \begin{figure*}
   \centering
   \includegraphics[angle=90,width=0.99\linewidth]{figures/ch4/II_radial_dependence}
   \caption{The dependence of $f_{\rm CGM}$ and $f_{\rm CNM} / f_{\rm Disk}$ on the radial position of each event at two different times in the evolution of the galaxy. The meaning of each point, the error bars, and colors are the same as in Figure~\ref{ch4:fig:CGM_CNM_variance}.}
   \label{ch4:fig:radial position}
 \end{figure*}

@@

 \begin{figure*}
   \centering
   \includegraphics[angle=90,width=0.99\linewidth]{figures/ch4/II_n_dependence}
   \caption{The variation of $f_{\rm CGM}$, $f_{\rm CNM} / f_{\rm Disk}$, and the spread of the metal fraction PDFs in the ISM as a function of the local ISM number density ($n$) within the injection region of the event just prior (within 0.1~Myr) of the event. Points, lines, and line colors mean the same as shown in Figure~\ref{ch4:fig:CGM_CNM_variance}}
   \label{ch4:fig:ISM_variance}
 \end{figure*}

@@

Finally, we examine the companion run (\runtwonu) to see if the global star formation rate of the galaxy drives variation in these results. Although this does not help to directly account for the variation seen in the previous plots, this could provide insight into how SFR (in an averaged sense) affects the evolution of metals. We note that correlation with SFR is of interest not because the formation of stars by themselves, but rather the increase in feedback associated with a higher SFR (and thus a warmer / hotter ISM, greater turbulence in the ISM, and more significant outflows). We compare these two runs in Figure~\ref{ch4:fig:SFR_comparison_CGM_CNM}, showing runs from \runonenu~ in green and runs at the lower SFR, \runtwonu, in purple. $f_{\rm CGM}$ increases much more rapidly across injection energies in \runonenu. However, this value seems to be similar across runs for E49 and E51 by $\sim$50 Myr, with an additional increase again in the \runonenu~ simulations towards the end of the time. This initial spike, lull, and second increase corresponds to the period of active star formation, slightly lull, and increase in SFR experienced during the \runonenu~ simulations (see Figure~\ref{ch1:figsfr_mass_evolution}; the lull occurs between 40 and 80 Myr after the enrichment events, or during 220 - 260 Myr in that figure). The SFR is consistently low (or zero) throughout \runtwonu, with just a couple brief increases in SFR. Although E49 and E51 exhibit similar behavior across global differences in SFR, the difference in E46 is significant throughout the examined time period. As these sources do not contain enough energy to eject their metals from the galaxy by themselves, they are only ejected from the galaxy by being swept up in the ISM during other feedback events. The evolution of these events are therefore much more dependent upon the global galaxy properties.

>>>>

\begin{figure*}
\centering
\includegraphics[width=0.45\linewidth]{figures/ch4/AGB1_enrichment_evolution_average_CGM}
\includegraphics[width=0.45\linewidth]{figures/ch4/NSNS1_enrichment_evolution_average_CGM} \\
\includegraphics[width=0.45\linewidth]{figures/ch4/SNE1_enrichment_evolution_average_CGM}
\includegraphics[width=0.45\linewidth]{figures/ch4/HNE1_enrichment_evolution_average_CGM}
\caption{Time evolution of the fraction of metals in each phase of the ISM (colored lines), the galaxy's disk (black, solid), and the CGM (black, dashed) as averaged across all events at a given $E_{\rm ej}$. The fractions are all normalized to the total amount of metals initially injected in each event, and the individual ISM phases (colored lines) sum to the black, solid line. \textbf{Need to remake these figures}}
\label{ch4:fig:ISM_CGM}
\end{figure*}

@@

However, the metals from each source do gradually trend towards a fraction of $\sim$0.8 by the end of the 150~Myr simulation time, corresponding to the mass fraction of the CNM at this point in the galaxy's evolution (see Figure~\ref{ch1:fig:ISM_evolution}). This trend -- that the fraction of metals contained in a given phases tends towards the mass fraction of that phase -- is true across all phases in the simulation. Therefore, we can consider that the metals for each source are well-mixed across the \textit{phases} of the ISM on timescales of $\sim$100-150~Myr. This is comparable, but less than, the dynamical timescale of the galaxy, $\sim$200~Myr. These two results suggest that the delay-time between when metals are available to enrich ongoing star formation is on order of $\sim$10~Myr across sources, and only significant for the lowest (E46, AGB-like) energy sources. Although well-mixed across phases, we emphasize that this does not imply that the abundances are the same across phases nor that the metals are spatially well-mixed across the galaxy. We investigate this second point further below.

@@

 \begin{figure*}
   \centering
   \includegraphics[angle=90,width=0.9\linewidth]{figures/ch4/II_radial_dependence}
   \caption{The dependence of $f_{\rm CGM}$ and $f_{\rm CNM} / f_{\rm Disk}$ on the radial position of each event at two different times in the evolution of the galaxy. The meaning of each point, the error bars, and colors are the same as in Figure~\ref{ch4:fig:CGM_CNM_variance}.}
   \label{ch4:fig:radial position}
 \end{figure*}

@@

 \begin{figure*}
   \centering
   \includegraphics[angle=90,width=0.9\linewidth]{figures/ch4/II_n_dependence}
   \caption{The variation of $f_{\rm CGM}$, $f_{\rm CNM} / f_{\rm Disk}$, and the spread of the metal fraction PDFs in the ISM as a function of the local ISM number density ($n$) within the injection region of the event just prior (within 0.1~Myr) of the event. Points, lines, and line colors mean the same as shown in Figure~\ref{ch4:fig:CGM_CNM_variance}}
   \label{ch4:fig:ISM_variance}
 \end{figure*}

@@

Finally, we examine the companion run (\runtwonu) to see if the global star formation rate of the galaxy drives variation in these results. Although this does not help to directly account for the variation seen in the previous plots, this could provide insight into how SFR (in an averaged sense) affects the evolution of metals. We note that correlation with SFR is of interest not because the formation of stars by themselves, but rather the increase in feedback associated with a higher SFR (and thus a warmer / hotter ISM, greater turbulence in the ISM, and more significant outflows). We compare these two runs in Figure~\ref{ch4:fig:SFR_comparison_CGM_CNM}, showing runs from \runonenu~ in green and runs at the lower SFR, \runtwonu, in purple. $f_{\rm CGM}$ increases much more rapidly across injection energies in \runonenu. However, this value seems to be similar across runs for E49 and E51 by $\sim$50 Myr, with an additional increase again in the \runonenu~ simulations towards the end of the time. This initial spike, lull, and second increase corresponds to the period of active star formation, slightly lull, and increase in SFR experienced during the \runonenu~ simulations (see Figure~\ref{ch1:fig:sfr_mass_evolution}; the lull occurs between 40 and 80 Myr after the enrichment events, or during 220 - 260 Myr in that figure). The SFR is consistently low (or zero) throughout \runtwonu, with just a couple brief increases in SFR. Although E49 and E51 exhibit similar behavior across global differences in SFR, the difference in E46 is significant throughout the examined time period. As these sources do not contain enough energy to eject their metals from the galaxy by themselves, they are only ejected from the galaxy by being swept up in the ISM during other feedback events. The evolution of these events are therefore much more dependent upon the global galaxy properties.
